### 2020-10-22 thesis/chap_1.tex
address comment 11

The ST-Sim model uses three states: Forest, Urban and Agriculture. Forest was further subdivided into classes of age and type, derived from the LANDIS outputs: three forest types (\textbf{deciduous}, \textbf{mixt}, and \textbf{coniferous}) and three age classes (\textbf{young}, \textbf{medium}, and \textbf{old}) for a total of 9 classes.
The model allows for 4 groups of transitions:
\begin{itemize}
\item{\textbf{Urbanisation}}: groups \textbf{deforestation} (Forest $\Rightarrow$ Urban) and \textbf{agricultural loss} (Agriculture $\Rightarrow$ Urban).
\item{\textbf{Agricultural expansion}} (Forest $\Rightarrow$ Agriculture).
\item{\textbf{Forest Internals}}: groups the 72 combinations of forest change between the 9 forest internal states.
\end{itemize}
The model takes in 3 different strata. A stratum in ST-Sim refers to a subset of the entire landscape being considered for analysis. Strata are typically used to divide the overall landscape into regions or zones, each of which can have different model parameters specified. The three stratum are:
\begin{itemize}
\item{Primary stratum:} delineates Montérégie from the  surrounding buffer and highlights protected areas.
\item{Secondary stratum:} delineates municipalities of the region, to allow to set targets specific to each municipality.
\item{Tertiary stratum:} delineates LANDIS land types, to allow to set transition multipliers for forest types that match the LANDIS simulations. \\
\end{itemize}

>>>>

The ST-Sim model uses three states: Forest, Urban and Agriculture. Forest was further subdivided into classes of age and type, derived from the LANDIS outputs: three forest types (\textbf{deciduous}, \textbf{mixt}, and \textbf{coniferous}) and three age classes (\textbf{young}, 0-20 yrs ; \textbf{medium}, 20-40 yrs ; and \textbf{old}, 40+ yrs) for a total of 9 classes.
The model allows for 4 groups of transitions:
\begin{itemize}
\item{\textbf{Urbanisation}}: groups \textbf{deforestation} (Forest $\Rightarrow$ Urban) and \textbf{agricultural loss} (Agriculture $\Rightarrow$ Urban).
\item{\textbf{Agricultural expansion}} (Forest $\Rightarrow$ Agriculture).
\item{\textbf{Forest Internals}}: groups the 72 combinations of forest change between the 9 forest internal states.
\end{itemize}
The model takes in 3 different strata. A stratum in ST-Sim refers to a subset of the entire landscape being considered for analysis. Strata are typically used to divide the overall landscape into regions or zones, each of which can have different model parameters specified. The three stratum are:
\begin{itemize}
\item{Primary stratum:} delineates Montérégie from the  surrounding buffer and highlights protected areas.
\item{Secondary stratum:} delineates municipalities of the region, to allow to set targets specific to each municipality.
\item{Tertiary stratum:} delineates LANDIS land types, to allow to set transition multipliers for forest types that match the LANDIS simulations. \\
\end{itemize}
